Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-12 ijar-npb-ms.tex
Update system in appendix to match new Figure 4.

\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t, s\,-\,1\,-\,4\,-\,5\,-\,t, 2:4\,-\,6\,-\,3:5)}
\begin{itemize}
  \item \texttt{s\,-\,1\,-\,2\,-\,3\,-\,t} signifies the route from left to right entering the first component and going across the top of the system block diagram in Figure \ref{fig:bridge-layout};
  \item \texttt{s\,-\,1\,-\,4\,-\,5\,-\,t} signifies the bottom route through the block diagram;
  \item \texttt{2:4\,-\,6\,-\,3:5} connects the top two components of type 3 to the bottom two components of type 3, signifying the bridge.
\end{itemize}
Naturally such as expression is not necessarily unique, so that completely equivalently one may write:

\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2:4\,-\,6\,-\,3:5\,-\,t, 2\,-\,3, 4\,-\,5)}

@@

\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1), "T2"=c(6),}

\noindent\texttt{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~"T3"=c(2,3,4,5)))}

>>>>

\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t, s\,-\,4\,-\,5\,-\,3\,-\,t, 1:4\,-\,6\,-\,2:5)}
\begin{itemize}
  \item \texttt{s\,-\,1\,-\,2\,-\,3\,-\,t} signifies the route from left to right entering the first component going across the top of the system block diagram in Figure \ref{fig:bridge-layout};
  \item \texttt{s\,-\,4\,-\,5\,-\,3\,-\,t} signifies the bottom route through the block diagram;
  \item \texttt{1:4\,-\,6\,-\,2:5} connects the top two components of type 3 to the bottom two components of type 3, signifying the bridge.
\end{itemize}
Naturally such as expression is not necessarily unique, so that completely equivalently one may write:

\noindent\texttt{sys <- graph.formula(s\,-\,1:4\,-\,6\,-\,2:5\,-\,3\,-\,t, 1\,-\,2, 4\,-\,5)}

@@

\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1,2,4,5), "T2"=c(6),}

\noindent\texttt{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~"T3"=c(3)))}
